### 2013-05-29 inst/examples/BUGS/parametric-vs-nonparametric.Rmd

```{r jags-setup}
y <- obs$x[-1] 
N <- length(y);
jags.data <- list("N","y")
n.chains <- 3
n.iter <- 1e5
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
```

@@

```{r common-priors}
stdQ_prior_p <- c(0.0001, 100)
stdR_prior_p <- c(0.0001, 100)
stdQ_prior  <- function(x) dunif(x, stdQ_prior_p[1], stdQ_prior_p[2])
stdR_prior  <- function(x) dunif(x, stdR_prior_p[1], stdR_prior_p[2])
```

@@

jags.inits <- function(){
  init_p = c(r0=1, K=10, theta=2)
  list("K"=init_p["K"] * rlnorm(1,0,.1),
       "logr0"=log(rlnorm(1,0,.1) ),
       "logtheta"=log(init_p["theta"] * rlnorm(1,0,.1)), 
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.1),
       "stdR"=sqrt(0.1) * rlnorm(1,0,.1),
       "x"=y,        
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

@@

#Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=10, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r ricker-mcmc, dependson="ricker-model"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ", "stdR")
jags.inits <- function(){
  list("K"=10 * rlnorm(1,0,.5),
       "logr0"=log(1) * rlnorm(1,0,.5),
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.5),
       "stdR"=sqrt(0.1) * rlnorm(1,0,.5),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=10, n.iter=n.iter, 
                            n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ", "stdR")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.5)), 
       "logK"=log(10* rlnorm(1,0,.5)),
       "logtheta" = log(5 * rlnorm(1,0,.5)),  
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.5),
       "stdR"=sqrt(0.1) * rlnorm(1,0,.5),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers.bugs")
myers_jags <- do.call(autojags, 
                      list(object=myers_jags, n.update=10, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

>>>>

```{r jags-setup}
y <- obs$x[-1] 
N <- length(y);
jags.data <- list("N"=N,"y"=y)
n.chains <- 6
n.iter <- 5e5
n.burnin <- floor(10000)
n.thin <- max(1, floor(n.chains * (n.iter - n.burnin)/1000))
n.update <- 10
```

@@

```{r common-priors}
stdQ_prior_p <- c(0.0001, 100)
stdR_prior_p <- c(1e-6, .1)
stdQ_prior  <- function(x) dunif(x, stdQ_prior_p[1], stdQ_prior_p[2])
stdR_prior  <- function(x) dunif(x, stdR_prior_p[1], stdR_prior_p[2])
```

@@

jags.inits <- function(){
  list("K"= 10 * rlnorm(1,0,.1),
       "logr0"=log(rlnorm(1,0,.5) ),
       "logtheta"=log(2 * rlnorm(1,0,.1)), 
       "stdQ"= 0.2 * rlnorm(1,0,.1),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,        
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

@@

#Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=n.update, 
                                     n.iter=n.iter, n.thin = n.thin))
```

@@

```{r ricker-mcmc, dependson="ricker-model"}
# Uniform priors on standard deviation terms
jags.params=c("K","logr0", "stdQ", "stdR")
jags.inits <- function(){
  list("K"= 10 * rlnorm(1,0,.5),
       "logr0" = log( rlnorm(1,0,.5) ),
       "stdQ"= 0.2 * rlnorm(1,0,.2),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345) 
ricker_jags <- do.call(jags.parallel, 
                       list(data=jags.data, inits=jags.inits, 
                            jags.params, n.chains=n.chains, 
                            n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,
                            model.file="ricker.bugs"))
recompile(ricker_jags)
ricker_jags <- do.call(autojags, 
                       list(object=ricker_jags, n.update=n.update, n.iter=n.iter, 
                            n.thin = n.thin, progress.bar="none"))
```

@@

```{r myers-mcmc, dependson="myers-model"}
jags.params=c("logr0", "logtheta", "logK", "stdQ", "stdR")
jags.inits <- function(){
  list("logr0" = log(rlnorm(1,0,.5)), 
       "logK" = log(10 * rlnorm(1,0,.2)),
       "logtheta" = log( 2 * rlnorm(1,0,.2)),  
       "stdQ"= 0.2 * rlnorm(1,0,.1),
       "stdR"= 1e-5 * rlnorm(1,0,.1),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers.bugs")
myers_jags <- do.call(autojags, 
                      list(object=myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```
